---
title: 'Radar Charts2'
author: "[Orhan Aktaş](https://www.linkedin.com/in/orhanaktas/)"
date: "10 June 2021"
output:
  html_document:
    theme: flatly
    df_print: paged
    number_sections: true
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r libraries, include=FALSE}
library(tidyverse)
library(readxl)
library(fmsb)
```

# Data import

import scores

```{r}
scores <- read_excel("C:/Users/user/Desktop/herşey/R_projects/radar_charts2/data/gesi_scores.xlsx")
```

# Data Preparation for Radar Chart function

The data should be organized as follow:

-   The row 1 must contain the maximum values for each variable

-   The row 2 must contain the minimum values for each variable

-   Data for cases or individuals should be given starting from row 3

-   The number of columns or variables must be more than 2.

```{r}
data<-scores %>% 
  select(-1,-2,-20)

data<-
  rbind(rep(2, 17),rep(-2,17)) %>% 
  as_tibble() %>% 
  set_names(names(data)) %>% 
  rbind(data)

```

## define helper function

```{r}
create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 0.7,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
    # Customize the grid
    cglcol = "grey", cglty = 1, cglwd = 0.8,
    # Customize the axis
    axislabcol = "grey", 
    # Variable labels
    vlcex = vlcex, vlabels = vlabels,
    caxislabels = caxislabels, title = title, ...
  )
}
```

## **Basic radar plot**

Plot the data for student 1

```{r}
first_row <- data %>% slice(1:3)
create_beautiful_radarchart(first_row)
```
