---
title: 'Radar Charts2'
author: "[Orhan Aktaş](https://www.linkedin.com/in/orhanaktas/)"
date: "10 June 2021"
output:
  html_document:
    theme: flatly
    df_print: paged
    number_sections: true
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r libraries, include=FALSE}
library(tidyverse)
library(readxl)
library(fmsb)
```

# Data import

import scores

```{r}
scores <- read_excel("C:/Users/user/Desktop/herşey/R_projects/radar_charts2/data/gesi_scores.xlsx")
```

# Data Preparation for Radar Chart function

The data should be organized as follow:

-   The row 1 must contain the maximum values for each variable

-   The row 2 must contain the minimum values for each variable

-   Data for cases or individuals should be given starting from row 3

-   The number of columns or variables must be more than 2.

```{r}
data<-scores %>% 
  select(-1,-2,-20)

data<-
  rbind(rep(2, 17),rep(-2,17)) %>% 
  as_tibble() %>% 
  set_names(names(data)) %>% 
  rbind(data)

```

## define helper function

```{r}
create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 0.3,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
    # Customize the grid
    cglcol = "grey", cglty = 1, cglwd = 0.8,
    # Customize the axis
    axislabcol = "grey", 
    # Variable labels
    vlcex = vlcex, vlabels = vlabels,
    caxislabels = caxislabels, title = title, ...
  )
}
```

## **Basic radar plot**

Plot the data for one project

```{r}
first_row <- data %>% slice(1:3)
create_beautiful_radarchart(first_row)
```

Reduce plot margin using par()

```{r}
op <- par(mar = c(0, 0, 0, 0))
create_beautiful_radarchart(first_row, caxislabels = c(-2, -1, 0, 1, 2))
par(op)
```

Create separated spider charts for each project.
First a trial for 3 projects.

```{r}
# get data
three_rows <- data %>% slice(1:5)

# Define colors and titles
colors <- c("#00AFBB", "#E7B800", "#FC4E07")
titles <- c("Project.1", "Project.2", "Project.3","Project.4", "Project.5", "Project.6")

# if we want to produce an output uncomment the line below and the line at the end of this chunk.
# png(filename = "output/charts_par_0303_1111_mfrow_32.png", width = 4.2, height = 5.94, units = "in", res = 1450)

# Reduce plot margin using par()
# Split the screen in 3 parts
op <- par(mar = c(0, 2, 2, 2))
op <- par(oma = c(1, 1, 1, 1))
par(mfrow = c(3,2))

# Create the radar chart
for(i in 1:6){
  create_beautiful_radarchart(
    data = data %>% slice(1,2,i+2), 
    caxislabels = c(-2, -1, 0, 1, 2),
    color = "#00AFBB", 
    title = titles[i],
    vlcex = 0.5
    )
}
par(op)

# if we want to produce an output uncomment the line below and the line starting with png.
# dev.off()
```
